---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# remr

<!-- badges: start -->
[![R-CMD-check](https://github.com/joshualerickson/remr/workflows/R-CMD-check/badge.svg)](https://github.com/joshualerickson/remr/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `remr` is to get transects along a linestring so that you can then perform a Relative Elevation Model. Thanks to [paleolimbot](https://gist.github.com/paleolimbot/d24df1a288f355f89b69eb664dc54882?permalink_comment_id=4052200#gistcomment-4052200) this process is now in a function!

## Contributions  

Contributions are welcome! Please if you have any ideas or recommendations submit an issue. Thanks. 

## Installation


To install the development version of the `remr` package, you can
install directly from [GitHub](https://github.com/):

``` r
# install.packages("devtools")
devtools::install_github("joshualerickson/remr")
```
## Example

This is a basic example which shows you how to solve a common problem: getting transects along a linestring and then extracting points on the linestring and transects.

```{r, eval=TRUE}

library(remr)

pts = matrix(c(170800,172000, 5410500, 5410400), 2)
line = sf::st_as_sf(sf::st_sfc(sf::st_linestring(pts), crs = 32612))

ele <- elevatr::get_elev_raster(line, z = 13)
terra::crs(ele) <- '+proj=utm +zone=12 +datum=WGS84 +units=m +no_defs'

rem <- get_transects(line, ele, distance = 100, length = 500)

 ele_crop <- terra::crop(terra::rast(ele), terra::vect(sf::st_buffer(line, 200)))
 terra::plot(ele_crop)
 plot(line$x, add = TRUE)
 plot(rem$geometry, add = TRUE)
```

